notes

### 2022-08-29 README.Rmd

>>>>

  <!-- badges: start -->
[![R-CMD-check](https://github.com/parkgayoung/CTtps/actions/workflows/render-in-docker.yaml/badge.svg)](https://github.com/parkgayoung/CTtps/actions/workflows/render-in-docker.yaml)
[![Launch Rstudio Binder](http://mybinder.org/badge_logo.svg)](https://mybinder.org/v2/gh/parkgayoung/CTtps/master?urlpath=rstudio)
  <!-- badges: end -->
